### 2022-05-10 supplement.Rmd
Fix typo in formula

  # Prior sensitivity analysis
  list(
    `$b_Intercept\\sim\\mathcal{U}(-10,10)$` = c(
      set_prior("uniform(-10, 10)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("cauchy(0, 0.3)", class = "sd")
    ),
    `b\\sim$\\mathcal{N}(0,0.2)$` = c(
      set_prior("normal(0, 0.2)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("cauchy(0, 0.3)", class = "sd")
    ),
    `$\\sigma\\sim\\mathcal{U}(0,10)$` = c(
      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("uniform(0, 10)", class = "sd")
    ),
    `$\\sigma\\sim\\text{Student-}t(10,0,0.2)$` = c(
      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("student_t(10, 0, 0.2)", class = "sd")
    )
  ) %>%
    map2_dfr(names(.), function(prior_sens, prior_name) {

>>>>

  # Prior sensitivity analysis
  list(
    `$b_Intercept\\sim\\mathcal{U}(-10,10)$` = c(
      set_prior("uniform(-10, 10)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("cauchy(0, 0.3)", class = "sd")
    ),
    `$b\\sim\\mathcal{N}(0,0.2)$` = c(
      set_prior("normal(0, 0.2)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("cauchy(0, 0.3)", class = "sd")
    ),
    `$\\sigma\\sim\\mathcal{U}(0,10)$` = c(
      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("uniform(0, 10)", class = "sd")
    ),
    `$\\sigma\\sim\\text{Student-}t(10,0,0.2)$` = c(
      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("student_t(10, 0, 0.2)", class = "sd")
    )
  ) %>%
    map2_dfr(names(.), function(prior_sens, prior_name) {
